\documentclass{article}

\usepackage[utf8]{inputenc}
\usepackage{fullpage}
\usepackage{times}
\usepackage{tcolorbox}
\usepackage{enumitem}
\usepackage{multicol}
\usepackage{bookmark}

\bookmarksetup{
  numbered, 
  open,
}

\setlist{itemsep=2pt}
\renewcommand{\thesection}{Chapter 6.\arabic{section}}
\renewcommand{\thesubsection}{6.\arabic{section}.\arabic{subsection}}
\setcounter{section}{3}

\begin{document}

\noindent
{CS 456 \hfill Hao Pan}\\
{Salahuddin, Mohammad}\\
{Spring 2018}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{center}
\section{Data Center Networking}
\noindent
\end{center}

\subsection{Data Center Networks}

\begin{itemize}
\item {\bf Data center networks} has 10s to 100s of thousands of hosts, and they are often closely coupled in close proximity.
\item e-businesses like Amazon, content-servers like YouTube or Microsoft, and search engines like Google are all examples of data center networks.
\item Data center networks have challenges in running multiple applications, since each is serving a massive number of clients.
\item It may also have trouble managing and balancing loads to avoid processing, networking, and data bottlenecks.
\item A {\bf load balancer}, in the application-layer, directs workload within the data center when external client requests are received. It also returns results to external clients so that data center internals are hidden from the client.
\item Data center networks have rich interconnection among switches, with hosts typically being stacked in {\bf racks}. The top of each rack \emph{contains a switch}, the {\bf Top of Rack (TOR) switch}, which interconnects hosts in the rack with each other and with other switches in the data center. This means that every host in the rack has a network interface card which connects to a TOR switch.
\item With so much interconnection, throughput between racks is increased, since multiple routing paths are possible. Reliability is also increased because of this reason.
\item See {\bf slide 5-60} for a diagram showing the connection between switches and racks in a data center network.
\end{itemize}

\end{document}