\documentclass[11pt]{article}

\usepackage{fullpage}
\usepackage{times}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{enumitem}

\setlist{itemsep=2pt}


\begin{document}

\noindent
{CS 456 \hfill Hao Pan}\\
{Salahuddin, Mohammad}\\
{Spring 2018}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{center}
\underline{\large \bf Chapter 1.1 - What is the Internet}\\

{\it The internet is the world's largest network system.}\\

\noindent
{\hfill 01/05/2018 [T]}
\end{center}

\underline{Technical Viewpoint}

\begin{itemize}
\item A {\bf host} or {\bf end system} is a device, usually a computer, in a network which offers {\it information}, {\it services}, or {\it applications} to users.
\item Communication is done through {\it links} such as: {\it fiber, copper, radio, satellite...}
\item {\bf Bandwidth} is the transmission rate across the link.
\item Data is transmitted via {\bf packet switching}, where they are forwarded in chunks called {\it packets}.
\begin{itemize}
\item Data is received by {\bf network nodes}, which are usually {\it routers} or {\it switches}.
\end{itemize}

\item {\bf Internet}: A "network of networks."
\begin{itemize}
\item Interconnected ISPs (Internet Service Providers).
\end{itemize}
\item {\bf Protocols} control {\it sending} and {\it receiving} of messages.
\begin{itemize}
\item {\bf Ex.} {\it TCP, IP, HTTP, Skype, 802.11}
\end{itemize}
\item The internet has {\it standards}:
\begin{itemize}
\item {\it Request for Comments} ({\bf RCF}): A publication from the {\it Internet Enginering Task Force} ({\bf IETF}) which describes behaviours and methods for making the Internet and connected systems work.
\end{itemize}
\end{itemize}

\underline{Service Viewpoint}

\begin{itemize}
\item The internet is an infrastructure that provides {\it services} to applications.
\begin{itemize}
\item {\bf Ex.} {\it Web, VoIP, email, games...}
\end{itemize}
\item It provides {\it programming interfaces} to apps.
\begin{itemize}
\item Uses {\it hooks}, which allow the sending and receiving of application programs to "connect" to the internet.
\end{itemize}
\item Must use a {\bf socket interface}: A set of rules that programs must abide by to deliver and receive data.
\end{itemize}

\newpage

\underline{What is a Protocol}

\begin{itemize}
\item Human Protocols:
\begin{itemize}
\item Questions (ex. "What is the time?")
\item Introductions
\end{itemize}
\item Network Protocols:
\begin{itemize}
\item Uses machines rather than humans
\item Communication activity in the Internet is governed by protocols.
\end{itemize}
\end{itemize}


\end{document}