\documentclass{article}

\usepackage[utf8]{inputenc}
\usepackage{fullpage}
\usepackage{times}
\usepackage{tcolorbox}
\usepackage{enumitem}
\usepackage{multicol}
\usepackage{bookmark}

\bookmarksetup{
  numbered, 
  open,
}

\setlist{itemsep=2pt}
\renewcommand{\thesection}{Chapter 4.\arabic{section}}
\renewcommand{\thesubsection}{4.\arabic{section}.\arabic{subsection}}
\setcounter{section}{3}

\begin{document}

\noindent
{CS 456 \hfill Hao Pan}\\
{Salahuddin, Mohammad}\\
{Spring 2018}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{center}
\section{Generalized Forward and SDN}
\noindent
\end{center}

\subsection{Overview}

\begin{itemize}
\item Each router contains a \emph{flow table} that is computed and distributed by a \emph{logically centralized} routing controller.
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{OpenFlow}

\subsubsection{Data Plane Abstraction}
\begin{itemize}
\item {\bf Flow} is defined by header fields.
\item {\bf Generalized forwarding} is a set of simple packet-handling rules:
\begin{itemize}
\item {\bf Pattern}: Match values in a packet's header fields.
\item {\bf Actions}: Drop, forward, and modify \emph{matched packets} or send them to the controller.
\item {\bf Priority}: Disambiguate overlapping patterns.
\item {\bf Counters}: \#bytes and \#packets.
\end{itemize}
\end{itemize}

\subsubsection{Flow Table Entries}
\begin{itemize}
\item OpenFlow has three sections for entries (more details on {\bf slide 4-62}):
\begin{itemize}
\item {\bf Rule}: A set of rules for the link layer, network layer, and transport layer (such as \emph{IP source, IP destination, etc...})
\item {\bf Action}: What to do with attached packet that matches provided rules.
\item {\bf Stats}: The packet itself and a byte counter.
\end{itemize}
\item Examples can be seen on {\bf slides 4-63 and 4-64}.
\end{itemize}

\subsubsection{OpenFlow Abstraction}
\begin{itemize}
\item {\bf match+action} unifies different kinds of devices.
\item Router:
\begin{itemize}
\item \emph{Match}: Longest destination IP prefix.
\item \emph{Action}: Forward out a link.
\end{itemize}
\item Switch:
\begin{itemize}
\item \emph{Match}: Destination MAC address.
\item \emph{Action}: Forward or flood.
\end{itemize}
\item Firewall:
\begin{itemize}
\item \emph{Match}: IP addresses and TCP/UDP port numbers.
\item \emph{Action}: Permit or deny.
\end{itemize}
\item NAT
\begin{itemize}
\item \emph{Match}: IP address and port.
\item \emph{Action}: Rewrite address and port.
\end{itemize}
\end{itemize}

\end{document}