\documentclass{article}

\usepackage[utf8]{inputenc}
\usepackage{fullpage}
\usepackage{times}
\usepackage{tcolorbox}
\usepackage{enumitem}
\usepackage{multicol}
\usepackage{bookmark}

\bookmarksetup{
  numbered, 
  open,
}

\setlist{itemsep=2pt}
\renewcommand{\thesection}{Chapter 4.\arabic{section}}
\renewcommand{\thesubsection}{4.\arabic{section}.\arabic{subsection}}
\setcounter{section}{0}

\begin{document}

\noindent
{CS 456 \hfill Hao Pan}\\
{Salahuddin, Mohammad}\\
{Spring 2018}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{center}
\section{Overview of Network Layer}
\noindent
\end{center}

\subsection{Overview}

\begin{itemize}
\item The network layer transports segments from the sending to the receiving host.
\item On the sending side, segments are encapsulated into datagrams.
\item On the receiving side, the segments are delivered to the transport layer.
\item The network layer protocols in \emph{every} host and router.
\item The router examines header fields in every IP datagram that passes through it.
\item The network layer has \emph{two key functions}:
\begin{itemize}
\item {\bf Forwarding}: Packets are moved from the router's input to its appropriate output.
\item {\bf Routing}: Determines the route taken by packets from its source to destination.
\end{itemize}
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Data Plane and Control Plane}

\begin{itemize}
\item The {\bf data plane}:
\begin{itemize}
\item Is a forwarding function.
\item Is a local, per-router function.
\item Determines how datagrams arriving to the router's input port is forwarded to its output port.
\end{itemize}
\item The {\bf control plane}:
\begin{itemize}
\item Is a network-wide logic.
\item Determines how datagrams are routed between routers along end-end paths from the source to destination host.
\item There are two approaches to the control plane:
\begin{itemize}
\item \emph{Traditional routing algorithms}, which is implemented in routers.
\item \emph{Software-defined networking (SDN)}, which is implemented in remote servers instead.
\end{itemize}
\end{itemize}
\item In a {\bf per-router control plane}, individual routing algorithms components in \emph{every router} interact in the control plane.
\item In a {\bf logically centralized control plane}, a distinct controller interacts with local control agents (CAs). The controller is usually remotely located.
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Network Service Model}

\begin{itemize}
\item Networks have certain \emph{service models} for transporting datagrams from a sender to the receiver.
\item For example, the service could guarantee delivery (within a certain time) for individual datagrams.
\item It could also guarantee in-order delivery, or delivery using the minimum required bandwidth, etc..
\end{itemize}

\end{document}